Universal Anonymous Signatures

### 2022-10-06 prism-backend/research/gsac/app-building-blocks.tex
Fixed some flaws. Still doing passes for minor checks.

>>>>

Modelling-wise, when using this extension, we need to refine also the
\oracle{BLIND} oracle used in the blindness game, so that besides the $\osmsg_0$
and $\osmsg_1$ messages to be signed in committed form, it also receives their
corresponding extended witnesses and statements. To prevent trivial wins, the
oracle aborts if any of the two options does not satisfy the relation. That is,
calls to this oracle are: $\oracle{BLIND}^\NIZKRel((\osmsg_0,x'_0,w'_0),
(\osmsg_1,x'_1,w'_1),\smsg)$. And, in case $((\smsg,x'_b),(\osmsg_b,w'_b))
\notin \NIZKRel$, for $b=0,1$, \oracle{BLIND} aborts. Otherwise, the output
is still $(\Ccom,\pi)$, for some ``extended'' $\pi$.

### 2022-10-06 prism-backend/research/gsac/app-uas-proofs.tex
Fixed some flaws. Still doing passes for minor checks.

  From an adversary \adv~against Game 2, we can build an adversary \advB against
  \SBCM's blindness property. The simulation that
  \advB does is straightforward. \advB runs Game 2 for \adv, randomly picking
  a number $q < n$, where $n$ is the number of users that \adv~creates via
  \HUGEN, and assigning to the $q$-th user the \vk key that \advB receives in
  its blindness game. Then, when \adv~makes a query to its \OBTCHALb oracle, if
  the chosen issuer is the $q$-th user, \advB forwards \adv's messages to its
  own \oracle{BLIND} oracle. Finally, \advB outputs \todo{XXXX UPDATE}
  whatever \adv~does. Note that, since in Game 2 we replace the \yissue value
  with a random value, and simulate the \RelIss proof, \adv~is not
  receiving information about the blindly signed messages beyond what \advB
  forwards from its own oracle. Thus, if \adv~wins in its game, \advB wins in
  its blindness game. However, since \advB has to guess the correct user
  that \adv~will use as issuer in its \OBTCHALb oracle, we have a $1/n$ security
  loss, where $n$ is the total number of users created by \adv.
  %
  \qed
\end{proof}

@@

  \paragraph{(d) All {\cred}s are bound to the \usk of a known \uid.} %
  \RelSig includes a condition that $\forall i\in[n], 
  \SBCMVerify(\ipk_i,\cred_i,\usk,\attrs_i) = 1$. Thus, simulation
  extractability of the NIZK for \RelSig and correctness of \SBCM, ensure that
  all credentials involved in the signature contain the same \usk as their user
  key  (first) attribute. Thus, either $\OWNR[\lbrace \cid_i \rbrace_{i\in[n]}]$
  returns some \uid in $\HU \cup \CU$, or it returns $\bot$ because no such
  \uid exists (but not because more than one \cid belongs to different {\uid}s).
  Assume that no such \uid exists. Then, the {$\cred_i$}s extracted by
  \ExtractSign cannot have been produced via a call to either \OBTISS or \ISSUE,
  since they only accept calls from known {\uid}s (either in \HU or \CU,
  respectively). Since, by simulation extractability of the NIZK for \RelSig at
  least one such credential must have been used to produce the signature, then
  this breaks the one-more forgery property of the underlying \SBCM.
  %
  \qed
\end{proof}

@@

\subsection{Security of $\CUASGen^{hide-iss}$}
\label{sapp:sec-hide-iss}

The only aspect that changes from \CUASGen to $\CUASGen^{hide-iss}$ is the
relationship used for signing, where we hide the specific issuer who produced
the (now only) credential used for signing.
%
This change does not affect the proofs for issuance anonymity, nor signature
anonymity.
%
Concerning unforgeability, note that the credential that is used to produce the
\UAS signature still needs to originate from a \uid in either \HU or \CU.
Otherwise, such credential, extracted by \ExtractSign, is a forgery and breaks
the one-more forgery property of \SBCM. Moreover, such credential must exist,
due to simulation extractability of the underlying NIZK.
%
The proof for non-frameability is also unaffected by the change.

Thus, if \CUASGen is a secure \UAS scheme, so is $\CUASGen^{hide-iss}$.

\subsection{Security of $\CUASGen^{int}$}
\label{sapp:sec-interactive}

\paragraph{Issuance Anonymity.} Since issuance anonymity is independent of
whether signature/authentication is interactive or not, the proof for issuance
anonymity in $\CUASGen^{int}$ is the same as for \CUASGen.

@@

\paragraph{Unforgeability and non-frameability.} The simulation described for
the anonymity case (i.e., \advB concatenating the random numbers
to the message to be signed by the oracle) applies here too. Since the
interactive protocol includes non-interactive proofs for the $\NIZKRel^{\Sign}$
and $\NIZKRel^{Open}$ relations, the proofs for unforgeability and
non-frameability of \CUASGen still apply.

>>>>

  From an adversary \adv~against game 2, we can build an adversary \advB against
  \SBCM's blindness property. The simulation that \advB does is straightforward.
  \advB runs game 2 for \adv, using the \SBCM \parm variable it receives, to
  set up the \SBCM instance for game 2. When \adv~makes a query to its \OBTCHALb
  oracle, \advB prepares a call to its $\oracle{BLIND}^\RelIss$ oracle, setting
  $\osmsg_b \gets \PRVUK[\cuid_b]$ as message to be blindly signed and
  accompanying each $\osmsg_b$ with its corresponding
  $(\cscid_{i,b},\ATTR[\cscid_{i,b}])$ (for all $i\in[n]$). In the response
  received from $\oracle{BLIND}^\RelIss$ (which succeeds in case both options
  are in \RelIss), \advB replaces the proof with a simulated one, and \yissue
  with a random value (as done in game 2). With the response from \adv, \advB
  completes the credential running \SBCMUnblind as usual. The rest of the
  simulation is as in game 2. Finally, \advB outputs whatever \adv~outputs.
  Again, zero-knowledge of the NIZK for \RelIss, and the fact that \fissue is
  \UAS-acceptable, ensure that simulation is correct, and \advB wins whenever
  \adv~does.
  %
  \qed
\end{proof}

@@

  \paragraph{(d) All {\cred}s are bound to the \usk of a known \uid.} %
  \RelSig includes a condition that $\forall i\in[n], 
  \SBCMVerify(\ipk_i,\cred_i,\usk,\attrs_i) = 1$. Thus, simulation
  extractability of the NIZK for \RelSig and correctness of \SBCM, ensure that
  all credentials involved in the signature contain the same \usk as their user
  key  (first) attribute. Thus, either $\OWNR[\lbrace \cid_i \rbrace_{i\in[n]}]$
  returns some \uid in $\HU \cup \CU$, or it returns $\bot$ because no such
  \uid exists (but not because more than one \cid belongs to different {\uid}s).
  Assume that no such \uid exists. Then, the {$\cred_i$}s extracted by
  \ExtractSign cannot have been produced via a call to either \OBTISS or \ISSUE,
  since they only accept calls from known {\uid}s (either in \HU or \CU,
  respectively). Since, by simulation extractability of the NIZK for \RelSig at
  least one such credential must have been used to produce the signature, then
  this breaks the one-more forgery property of the underlying \SBCM scheme.

  \paragraph{(e) All used credentials have been honestly issued.} %
  Finally, assume that there exists some $\cred_i$ among the ones used to
  produce the signature such that the credential is valid (i.e., \VerCred
  returns $1$ for the extracted values), but no matching entry exists in
  $\CRED[\cid]$. This means that the credential is a valid signature by the
  honest issuer with public key $\ipk_i$, but it was not produced via a call
  to \OBTISS or \ISSUE. Thus, it directly breaks the one-more forgery property
  of the underlying \SBCM scheme.
  %
  \qed
\end{proof}

@@

\subsection{Security of \CUASGenHideIss}
\label{sapp:sec-hide-iss}

The only aspect that changes from \CUASGen to \CUASGenHideIss is the
relationship used for signing, where we hide the specific issuer who produced
the (now only) credential used for signing.
%
This change does not affect the proofs for issuance anonymity, nor signature
anonymity.
%
Issuance unforgeability is also unaffected by the change. Concerning signature
unforgeability, note that the credential that is used to produce the \UAS
signature still needs to originate from a \uid in either \HU or \CU.
Otherwise, such credential, extracted by \ExtractSign, is a forgery and breaks
the one-more forgery property of \SBCM. Moreover, such credential must exist,
due to simulation extractability of the underlying NIZK.
%
The proof for non-frameability is also unaffected by the change.

Thus, if \CUASGen is a secure \UAS scheme, so is \CUASGenHideIss.

\subsection{Security of \CUASGenInt}
\label{sapp:sec-interactive}

\paragraph{Issuance Anonymity.} Since issuance anonymity is independent of
whether signature/authentication is interactive or not, the proof for issuance
anonymity in \CUASGenInt is the same as for \CUASGen.

@@

\paragraph{Unforgeability and non-frameability.} The simulation described for
the anonymity case (i.e., \advB concatenating the random numbers
to the message to be signed by the oracle) applies here too. Since the
interactive protocol includes non-interactive proofs for the \RelSig
and \RelIns relations, the proofs for unforgeability and
non-frameability of \CUASGen still apply.

### 2022-10-06 prism-backend/research/gsac/formal-uas.tex
Fixed some flaws. Still doing passes for minor checks.

Signature unforgeability, \ExpForgeSign, is mainly a combination (and
generalisation) of known requirements in AC and GS schemes. Namely, the
adversary is required to output a valid signature, from which we extract the
user key pair, credentials, $\yeval^1$ and \yinsp values used to generate the
signature. The adversary wins if the signature: (1) opens to a wrong value, or
to a value that cannot be processed by \Judge; (2), is not consistent with the
expected $\Yeval = (\yeval^0,\yeval^1)$ value; or (3), cannot be associated to
credentials owned by a known user. Here, we need to assume honest issuers.
Otherwise, it is trivial for the adversary to produce untraceable credentials
(i.e., that do not appear in any ``log'') which then evaluate to any desired
value when used to generate a signature.

@@

We thus extend unforgeability of signatures with issuance unforgeability,
\ExpForgeIssue. It captures that all honestly issued credentials meet the
requirements set by the corresponding issuer, and that any further credential
involved in the request is a valid credential, bound to the same known user. For
this, we allow the adversary \adv~to interact with the oracles (restricted to
honest issuers). Eventually, \adv~is challenged to output a credential \Cred
from which we extract the actual witnesses used in the credential request
associated to \cid. \adv~wins if the issuance function, applied to the extracted
values, does not meet the expected output, if not all of the credentials (if
any) used to endorse the request belong to the same (known) user to whom the new
credential was issued, or if any of such credentials is a forgery. Note that the
issuance transcript associated to the credential output by the adversary must
exist, as we unavoidably need to restrict to honest issuers. Indeed, a dishonest
issuer cannot be trusted to enforce any policy, nor to properly keep all
transcripts.

We formalise both properties in \figref{fig:exp-uas-unfor}.

@@

\begin{figure}[htp!]
  \centering
  \hspace*{-2em}
  \scalebox{0.85}{
    \begin{minipage}[t]{0.7\textwidth}
      \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        (\cid,\attrs,\cred,\ipk) \gets \adv^{\Oforge}(\parm) \\
        \pcif \ISR[\cid] \notin \HI \lor \trans[\cid] = \bot: \pcreturn 0 \\
        (\utrans,\yissue) \gets \trans[\cid] \\
        (\upk,\usk,\lbrace \Cred_i \rbrace_{i\in[n]}, \Cred)
        \gets \ExtractIssue(\trap,\utrans) \\
        \forall i\in[n], (\cid_i,\attrs_i,\cred_i,\ipk_i) \gets \C_i \\
        (\cid,\attrs,\cred,\ipk) \gets \C;
        \scid \gets \lbrace \cid_i \rbrace_{i\in[n]} \cup
        \lbrace \cid \rbrace \\
        \pcif \VerCred(\usk,\cid,\attrs,\cred,\ipk) = 0~\lor \\
        \pcind \fissue(\upk,\cid,\attrs,\lbrace (\cid_i,\attrs_i)
        \rbrace_{i\in[n]}) \neq \yissue~\lor \\
        \pcind \OWNR[\scid] \notin \HU \cup \CU: \pcreturn 1 \\        
        \pcif \exists i\in[n]~\suchthat~
        \VerCred(\usk,\cid_i,\attrs_i,\cred_i,\ipk_i) = 0~\lor \\
        \pcind (\exists \iid\in\HI~\suchthat~\PUBIK[\iid] = \ipk_i \land
        \CRED[\cid_i] = \bot~\land \\
        \pcind \VerCred(\usk,\cid_i,\attrs_i,\cred_i,\ipk_i) = 1):
        \pcreturn 1 \\        
        \pcreturn 0
        %
        \iffalse
        \cid \gets \adv^{\Oforge}(\parm) \\
        \pcif \ISR[\cid] \notin \HI \lor \trans[\cid] = \bot: \pcreturn 0 \\
        (\utrans,\yissue) \gets \trans[\cid] \\
        (\upk,\cdot,\lbrace (\cid_i,\attrs_i,\cred_i,\ipk_i) \rbrace_{i\in[n]},
        \cdot,\attrs,\cdot,\cdot) \\
        \pcind \gets \ExtractIssue(\trap,\utrans) \\
        \textrm{Let $\scid \gets \lbrace \cid_i \rbrace_{i\in[n]} \cup
          \lbrace \cid \rbrace$} \\
        \pcreturn \OWNR[\scid] \notin \HU \cup \CU~\lor \\
        \pcind \fissue(\upk,\cid,\attrs,\lbrace (\cid_i,\attrs_i)\rbrace_{i\in[n]})
        \neq \yissue
        \fi
      }      
    \end{minipage}    
    \begin{minipage}[t]{0.6\textwidth}
      \procedure[linenumbering=on]{$\ExpForgeSign(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        (\oid,\siid,\Sig=(\sig,\tyeval^0),\msg,\feval) \gets \adv^{\Oforge}(\parm) \\
        \pcif \exists \iid \in \siid~\suchthat~\iid \notin \HI~\lor \\
        \pcind \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
        \SIG[\uid]~\lor  \\
        \pcind \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0: \\
        \pcind \pcreturn 0 \\
        (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
	(\upk,\usk,\lbrace(\cid_i,\attrs_i,\cred_i)\rbrace_{i\in[n]},
        \tyeval^1,\tyinsp) % \pcskipln
        \\
        \pcind \gets \ExtractSign(\trap,\Sig) \\
        (\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]}, \msg) \\
        \pcreturn \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \notin
        \HU \cup \CU~\lor \\
        \pcind \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,
        \msg,\feval) = 0~\lor \\
        \pcind \yeval^0 \neq \tyeval^0 \lor \yeval^1 \neq \tyeval^1 \lor
        \yinsp \neq \tyinsp~\lor\\
        \pcind \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]},\msg) \neq \yinsp 
      }
    \end{minipage}
  }
  \caption{Unforgeability experiments in \UAS schemes.
    $\Oforge \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\OO,\UU\rbrace
    \CORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$. % In line 10 of \ExpForgeIssue, we
    % slightly abuse notation to denote that user \uid does not own a set of
    % credentials with {\cid}s and attributes equal to $\lbrace (\cid_i,\attrs_i)
    % \rbrace_{i\in[n]}$.
  }
  \label{fig:exp-uas-unfor}
\end{figure}

>>>>

Signature unforgeability, \ExpForgeSign (see \figref{fig:exp-uas-unfor}),
is a combination (and
generalisation) of known requirements in AC and GS schemes. Namely, the
adversary is required to output a valid signature, from which we extract the
user key pair, credentials, $\yeval^1$ and \yinsp values used to generate the
signature. The adversary wins if the signature: (1) opens to a wrong value, or
to a value that cannot be processed by \Judge; (2), is not consistent with the
expected $\Yeval = (\yeval^0,\yeval^1)$ value; or (3), cannot be associated to
credentials owned by a known user. Here, we need to assume honest issuers.
Otherwise, it is trivial for the adversary to produce untraceable credentials
(i.e., that do not appear in any ``log'') which then evaluate to any desired
value when used to generate a signature.

@@

We thus extend unforgeability of signatures with issuance unforgeability,
\ExpForgeIssue (see \figref{fig:exp-uas-unfor}). It captures that all honestly
issued credentials meet the requirements set by the corresponding issuer, and
that any further credential
involved in the request is a valid credential, bound to the same known user. For
this, we allow the adversary \adv~to interact with the oracles (restricted to
honest issuers). Eventually, \adv~is challenged to output a credential \Cred
from which we extract the actual witnesses used in the credential request
associated to \cid. \adv~wins if the issuance function, applied to the extracted
values, does not meet the expected output, if not all of the credentials (if
any) used to endorse the request belong to the same (known) user to whom the new
credential was issued, or if any of such credentials is a forgery. Note that the
issuance transcript associated to the credential output by the adversary must
exist, as we unavoidably need to restrict to honest issuers. Indeed, a dishonest
issuer cannot be trusted to enforce any policy, nor to properly keep all
transcripts.

@@

\begin{figure}[htp!]
  \centering
  \hspace*{-2em}
  \scalebox{0.8}{
    \begin{minipage}[t]{0.67\textwidth}
      \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        (\cid,\attrs,\cred,\ipk) \gets \adv^{\Oforge}(\parm) \\
        \pcif \ISR[\cid] \notin \HI \lor \trans[\cid] = \bot: \pcreturn 0 \\
        (\utrans,\yissue) \gets \trans[\cid] \\
        (\upk,\usk,\lbrace \Cred_i \rbrace_{i\in[n]}, \Cred)
        \gets \ExtractIssue(\trap,\utrans) \\
        \forall i\in[n], (\cid_i,\attrs_i,\cred_i,\ipk_i) \gets \C_i \\
        (\cid,\attrs,\cred,\ipk) \gets \C;
        \scid \gets \lbrace \cid_i \rbrace_{i\in[n]} \cup
        \lbrace \cid \rbrace \\
        \pcif \VerCred(\usk,\cid,\attrs,\cred,\ipk) = 0~\lor \\
        \pcind \fissue(\upk,\cid,\attrs,\lbrace (\cid_i,\attrs_i)
        \rbrace_{i\in[n]}) \neq \yissue~\lor \\
        \pcind \OWNR[\scid] \notin \HU \cup \CU: \pcreturn 1 \\        
        \pcif \exists i\in[n]~\suchthat~
        \VerCred(\usk,\cid_i,\attrs_i,\cred_i,\ipk_i) = 0~\lor \\
        \pcind (\exists \iid\in\HI~\suchthat~\PUBIK[\iid] = \ipk_i \land
        \CRED[\cid_i] = \bot~\land \\
        \pcind \VerCred(\usk,\cid_i,\attrs_i,\cred_i,\ipk_i) = 1):
        \pcreturn 1 \\        
        \pcreturn 0
        %
        \iffalse
        \cid \gets \adv^{\Oforge}(\parm) \\
        \pcif \ISR[\cid] \notin \HI \lor \trans[\cid] = \bot: \pcreturn 0 \\
        (\utrans,\yissue) \gets \trans[\cid] \\
        (\upk,\cdot,\lbrace (\cid_i,\attrs_i,\cred_i,\ipk_i) \rbrace_{i\in[n]},
        \cdot,\attrs,\cdot,\cdot) \\
        \pcind \gets \ExtractIssue(\trap,\utrans) \\
        \textrm{Let $\scid \gets \lbrace \cid_i \rbrace_{i\in[n]} \cup
          \lbrace \cid \rbrace$} \\
        \pcreturn \OWNR[\scid] \notin \HU \cup \CU~\lor \\
        \pcind \fissue(\upk,\cid,\attrs,\lbrace (\cid_i,\attrs_i)\rbrace_{i\in[n]})
        \neq \yissue
        \fi
      }      
    \end{minipage}    
    \begin{minipage}[t]{0.6\textwidth}
      \procedure[linenumbering=on]{$\ExpForgeSign(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        (\oid,\siid,\Sig=(\sig,\tyeval^0),\msg,\feval) \gets \adv^{\Oforge}(\parm) \\
        \pcif \exists \iid \in \siid~\suchthat~\iid \notin \HI~\lor \\
        \pcind \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
        \SIG[\uid]~\lor  \\
        \pcind \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0: \\
        \pcind \pcreturn 0 \\
        (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
	(\upk,\usk,\lbrace(\cid_i,\attrs_i,\cred_i)\rbrace_{i\in[n]},
        \tyeval^1,\tyinsp) % \pcskipln
        \\
        \pcind \gets \ExtractSign(\trap,\Sig) \\
        (\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]}, \msg) \\
        \pcreturn \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \notin
        \HU \cup \CU \lor (\exists i\in[n]~\suchthat \\
        \pcind \VerCred(\usk,\cid_i,\attrs_i,\cred_i,\ipk_i)=1 \land
        \CRED[\cid] = \bot)~\lor \\
        \pcind \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,
        \msg,\feval) = 0~\lor \\
        \pcind \yeval^0 \neq \tyeval^0 \lor \yeval^1 \neq \tyeval^1 \lor
        \yinsp \neq \tyinsp~\lor\\
        \pcind \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]},\msg) \neq \yinsp 
      }
    \end{minipage}
  }
  \caption{Unforgeability experiments in \UAS schemes.
    $\Oforge \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\OO,\UU\rbrace
    \CORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$. % In line 10 of \ExpForgeIssue, we
    % slightly abuse notation to denote that user \uid does not own a set of
    % credentials with {\cid}s and attributes equal to $\lbrace (\cid_i,\attrs_i)
    % \rbrace_{i\in[n]}$.
  }
  \label{fig:exp-uas-unfor}
\end{figure}
